MaxEnt: What is it good for?

### 2015-07-28 ms.tex
Sentences

has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.

>>>>

There are several possible reasons for the lack of consensus.

has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists, raised on \citet{jaynes},
to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.
